Algebraic File Synchronization: Adequacy and Completeness

### 2016-10-08 p2/axioms.tex
New notation for commands

So that we can describe the effects of commands in general,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we will investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
For example, we will write
$S=\cbdaa{n}{\vald}\cc\cbfaa{m}{\valf}$, or $S'=S\cc\cbba{o}$.
% monoid, but not free monoid
% monoid: semigroup with identity element
% Sequences of commands form a free semigroup
Sequences of commands form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which by definition leaves all filesystems unchanged.
\end{mydef}

@@

\begin{mydef}[$\eqext$]
% Relation in the algebra
$A\eqext B$ means that $B$ extends $A$,
% intended interpretation:
that is, they behave in the same way
on any filesystem $A$ does not break:
$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\aFS=B\aFS$.
% old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\eqext T$.
% preorder: reflexive and transitive
In other words, $\eqext$ is a preorder, and also a precongruence.
\end{mydef}

@@

\noindent
Pairs of commands in general have the form
\[ \cxynv\cc  \czwmv \]
where $X,Y,Z,W\in\typeset$, $n,m\in\setn$, 
and values are of the appropriate type: 
$\valvy\in\setvx{Y}$ and $\valvw\in\setvx{W}$.

@@

\begin{myax}\label{ax_same_breaks}
Commands on the same node break every filesystem if their types are incompatible:
$\cxynv\cc\czwnv \equiv \cbrk$ where $Y\ne Z$.
\end{myax}

\begin{myax}\label{ax_same_emptyseq}
Commands on the same node simplify:
$\cxynv\cc\czwnv \eqext \emptyseq$ where $Y=Z$, and $\cxw=\cbb$ 
or $\cxw=\cdd$.
\end{myax}

\begin{myax}\label{ax_same_singlec}
Commands on the same node simplify:
$\cxynv\cc \czwnv \equiv \cxwnv$ where $Y=Z$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
\end{myax}

@@

\begin{mydef}[Construction pair]
A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ 
and the commands are one
of the following:
   \begin{gather*}
            \cbdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
            \cbdaa{\nn}{\vald}\cc  \cbdaa{n}{\vald} \\
            \cfdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
            \cfdaa{\nn}{\vald}\cc  \cbdaa{n}{\vald}
   \end{gather*}
\end{mydef}

@@

\begin{mydef}[Destruction pair]
A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parent(n)=\nn$ and the commands are one
of the following:
   \begin{gather*}
            \cfba{n}\cc  \cdba{\nn} \\
            \cfba{n}\cc  \cdfaa{\nn}{\valf} \\
            \cdba{n}\cc  \cdba{\nn} \\
            \cdba{n}\cc  \cdfaa{\nn}{\valf}
   \end{gather*}
\end{mydef}

@@

\begin{mydef}[Assertion command]
A command is an assertion command if
for every filesystem it either breaks it or leaves it in the same state.
In other words, assertion commands have the same input and output type,
and there must also be only one possible value for their output.
Accordingly, $\cbba{n}$ and $\cdda{n}$ are the only two assertion commands.
\end{mydef}

@@

\begin{myax}\label{ax_assert}
Assertion commands can be removed:
$\cxynv \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
\end{myax}

@@

If $n=m$, then from \cref{ax_same_breaks} we know $Y=Z$ and $W=X$
as otherwise the commands, in one order or the other, would break all filesystems
and they could not be independent.
The commands are not assertion commands, and so from \cref{ax_same_singlec}
we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $Y=W$ and $\valvy=\valvw$.
Therefore $X=Y=Z=W$ which is only possible if both commands are $\cff$ and have the same
output value. This, however, contradicts our assumption that they are different.

>>>>

So that we can describe the effects of commands in general,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we will investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
For example, we will write
$S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
% monoid, but not free monoid
% monoid: semigroup with identity element
% Sequences of commands form a free semigroup
Sequences of commands form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which by definition leaves all filesystems unchanged.
\end{mydef}

@@

\begin{mydef}[$\eqext$]
% Relation in the algebra
$A\eqext B$ means that $B$ \emph{extends} $A$,
% intended interpretation:
that is, they behave in the same way
on any filesystem $A$ does not break:
$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\aFS=B\aFS$.
% old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\eqext T$.
% preorder: reflexive and transitive
In other words, $\eqext$ is a preorder, and also a precongruence.
\end{mydef}

@@

\noindent
Pairs of commands in general have the form
\[ \cxynv\cc  \czwmv \]
where $x,y,z,w\in\setv$ and $n,m\in\setn$.

@@

\begin{myax}\label{ax_same_breaks}
Commands on the same node break every filesystem if their types are incompatible:
$\cxynv\cc\czwnv \equiv \cbrk$ where $[y]\ne [z]$.
\end{myax}

\begin{myax}\label{ax_same_emptyseq}
Commands on the same node simplify:
$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$, and $\cxw=\cbb$ 
or $\cxw=\cdd$.
\end{myax}

\begin{myax}\label{ax_same_singlec}
Commands on the same node simplify:
$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
\end{myax}

@@

\begin{mydef}[Construction pair]
A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ 
and the commands are one
of the following:
   \begin{gather*}
            \cbdaa{\nn}\cc  \cbfaa{n} \\
            \cbdaa{\nn}\cc  \cbdaa{n} \\
            \cfdaa{\nn}\cc  \cbfaa{n} \\
            \cfdaa{\nn}\cc  \cbdaa{n}
   \end{gather*}
\end{mydef}

@@

\begin{mydef}[Destruction pair]
A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parent(n)=\nn$ and the commands are one
of the following:
   \begin{gather*}
            \cfba{n}\cc  \cdba{\nn} \\
            \cfba{n}\cc  \cdfaa{\nn} \\
            \cdba{n}\cc  \cdba{\nn} \\
            \cdba{n}\cc  \cdfaa{\nn}
   \end{gather*}
\end{mydef}

@@

\begin{mydef}[Assertion command]
A command is an assertion command if
for every filesystem it either breaks it or leaves it in the same state.
In other words, assertion commands have the same input and output type,
and there must also be only one possible value for their output.
Accordingly, $\cbba{n}$ and $\cdda{n}$ are the only two types of assertion commands.
\end{mydef}

@@

\begin{myax}\label{ax_assert}
Assertion commands can be removed:
$\cdda{n}\eqext\emptyseq$ and $\cbba{n}\eqext\emptyseq$.
% $\cxynv \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
\end{myax}

@@

If $n=m$, then from \cref{ax_same_breaks} we know $[y]=[z]$ and $[w]=[x]$
as otherwise the commands, in one order or the other, would break all filesystems
and they could not be independent.
The commands are not assertion commands, and so from \cref{ax_same_singlec}
we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $y=w$.
Therefore $[x]=[y]=[z]=[w]$ which is only possible if both commands are $\cff$ and have the same
output value. This, however, contradicts our assumption that they are different.

### 2016-10-08 p2/def-commands.tex
New notation for commands

Let us consider what kind of information is usually encoded in filesystem operations.
A minimal set of commands, based on the most frequent tools implemented by filesystems,
may be the following, where 
$n\in\setn$ and $\valv\in\setv$ (but $\valv\neq\empt$):
\begin{itemize}
\item $create(n,\valv)$, which creates a file or directory ($\valv$) at $n$
where the file system contains no file or directory ($\empt$);
\item $edit(n,\valv)$, which replaces the earlier file or directory at $n$ with $\valv$;
\item $remove(n)$, which removes the file or directory at $n$, and replaces it with $\empt$.
\end{itemize}
Regarding their output, that is, the state of the filesystem at $n$
after applying the command,
we know that after $create$ or $edit$, $\FS(n)\neq\empt$, whereas after $remove$,
$\FS(n)$ will be $\empt$. 
However, from \cite{NREC} and \cite{CBNR} we know that a useful set of axioms
will in some cases need to distinguish between, for example,
$edit$s that result in directories ($edit(n,\vald)$) and
ones that result in files ($edit(n,\valf)$), and treat them as separate commands,
as their behaviors are quite different when combined with other commands.
Indeed, Bill Zissimopoulos' work
demonstrated \cite{BZ}
that extending this distinction to more commands ultimately simplifies
the definition of conflicting commands, as our model will then able to predict the behavior of commands
more precisely.
In other words, encoding the type of the output ($\cchard$, $\ccharf$ or $\ccharb$) in the commands is definitely useful.
At the same time, there is never any need to consider the
exact output \emph{value} of a command,
as the success or failure of filesystem commands only depends on the types of values in the filesystem.

Notice, however, that the commands listed above also encode some information about 
their input, the state of the filesystem
before the command is applied. In particular, $create(n,\valv)$ requires that there are no files
or directories at $n$, while $edit(n,\valv)$ and $remove(n)$ require the opposite.
This creates an arbitrary asymmetry where
there is now more information available about their output than about their input.
As, based on the above, we expect that encoding more information in the commands
results in a model with greater predictive powers,
and in order to resolve this asymmetry, 
we propose a set of commands that encode
the type of the original state of $\FS(n)$ as well.
(Some real-life filesystem commands like $rmdir$ do this already.)

\begin{mydef}[Regular commands]
Therefore we have four pieces of information related to each command,
and represent them using quadruples that list
their input type ($X$), output type ($Y$),
the node to which they are applied ($n$),
and the value they store at the node ($\valvy$):
\[ \cxynv, \]
where $\valvy\in\setvx{Y}$.

We use $\cchard$, $\ccharf$ or $\ccharb$ to represent the different
types, and omit the final value if it is determined by the output type
(when it is $\empt$ or $\vald$).
For example, $\cbfaa{n}{\valf}$ will represent $create(n,\valf)$,
and $\cdba{n}$ will represent $rmdir(n)$.
\end{mydef}

@@

We note that a command or a sequence of commands is applied to a filesystem
by prefixing the command or sequence to it, for example: $\cbrk\aFS$, $\cbdaa{n}{\vald}\aFS$, 
or $S\aFS$ if $S$ is a sequence of commands.

\begin{mydef}[Effect of commands]
We use a replacement operator of the form
$\FS[\valv/n]$ to denote a filesystem derived from $\FS$ 
by replacing its value at $n$ with $\valv$:
\[ \FS[\valv/n](m) =
   \begin{cases}
   \valv &\mbox{if~} m=n\\
   \FS(m) &\mbox{otherwise.}
   \end{cases}
\]
The effect of the commands is then as follows:
\begin{align*}
&\cbrk\aFS = \fsbroken \\
&\cxynv\aFS = 
   \begin{cases}
   \fsbroken &\mbox{if~} \FS=\fsbroken\\
   \fsbroken &\mbox{if~} \FS(n)\not\in\setvx{X}\\
   \fsbroken &\mbox{if~} \FS[\valvy/n] \mbox{~violates the tree property}\\
   \FS[\valvy/n] &\mbox{otherwise.}
   \end{cases}
\end{align*}
\end{mydef}

In general, when we describe multiple or unknown commands, we may substitute one or both
of their types with variables, as we did with $\cxynv$. In this context,
if we write that $\cxy=\czw$, we mean that the input and output types
of the commands are the same ($X=Z$ and $Y=W$), while a full equality 
($\cxynv=\czwmv$)
implies
that their nodes and output values are also the same.

>>>>

Let us consider what kind of information is usually encoded in filesystem operations.
A minimal set of commands, based on the most frequent tools implemented by filesystems,
may be the following, where 
$n\in\setn$ and $\valv\in\setv$ (but $\valv\neq\empt$):
\begin{itemize}
\item $create(n,\valv)$, which creates a file or directory ($\valv$) at $n$
where the file system contains no file or directory ($\empt$);
\item $edit(n,\valv)$, which replaces the earlier file or directory at $n$ with $\valv$;
\item $remove(n)$, which removes the file or directory at $n$, and replaces it with $\empt$.
\end{itemize}
Regarding their output, that is, the state of the filesystem at $n$
after applying the command,
we know that after $create$ or $edit$, $\FS(n)\neq\empt$, whereas after $remove$,
$\FS(n)$ will be $\empt$. 
However, from \cite{NREC} and \cite{CBNR} we know that a useful set of axioms
will in some cases need to distinguish between, for example,
$edit$s that result in directories ($edit(n,\vald)$) and
ones that result in files ($edit(n,\valf)$), and treat them as separate commands,
as their behaviors are quite different when combined with other commands.
Indeed, Bill Zissimopoulos' work
demonstrated \cite{BZ}
that extending this distinction to more commands ultimately simplifies
the definition of conflicting commands, as our model will then able to predict the behavior of commands
more precisely.
In other words, encoding the outputvalue in the commands is definitely useful.
As the success or failure of filesystem commands only depends on the types of values in the filesystem,
we expect to use the type of their output when modelling their behavior.

Notice, however, that the commands listed above also encode some information about 
their input, the state of the filesystem
before the command is applied. In particular, $create(n,\valv)$ requires that there are no files
or directories at $n$, while $edit(n,\valv)$ and $remove(n)$ require the opposite.
This creates an arbitrary asymmetry where
there is now more information available about their output than about their input.
As, based on the above, we expect that encoding more information in the commands
results in a model with greater predictive powers,
and in order to resolve this asymmetry, 
we propose a set of commands that encode
the type of the original value $\FS(n)$ as well.
(Some real-life filesystem commands like $rmdir$ do this already.)
Again, as the success of failure of commands depends on types of values,
it is not necessary to encode the actual input value.
For example, the behavior of two commands that differ only in what the original file contains
that they overwrite is never going to be different.

\begin{mydef}[Regular commands]
Therefore we have three pieces of information related to each command,
and represent them using triples that contain
their input type ($[v_{in}]$), output value ($v_{out}$),
and the node to which they are applied ($n$):
\[ \caaaa{v_{in}}{v_{out}}{n}. \]
\end{mydef}

For example, $\cbfaa{n}$ will represent $create(n,\valf)$,
and $\cdba{n}$ will represent $rmdir(n)$.
When describing unknown commands, we substitute one or both
of their values with variables, and write e.g. $\cxynv$.
By $\cxynv=\czwmv$ we mean that the commands are identical
($[x]=[z]$ and $y=z$ and $n=m$).
As suggested above, we will frequently only investigate
the types of the input and output values of a command
(its input and output types), and write
$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$.

@@

We note that a command or a sequence of commands is applied to a filesystem
by prefixing the command or sequence to it, for example: $\cbrk\aFS$, $\cbdaa{n}\aFS$, 
or $S\aFS$ if $S$ is a sequence of commands.

\begin{mydef}[Effect of commands]
We use a replacement operator of the form
$\FS_{[\valv/n]}$ to denote a filesystem derived from a non-broken $\FS$ 
by replacing its value at $n$ with $\valv$:
\[ \FS_{[\valv/n]}(m) =
   \begin{cases}
   \valv &\mbox{if~} m=n\\
   \FS(m) &\mbox{otherwise.}
   \end{cases}
\]
The effect of the commands is then as follows:
\begin{align*}
&\cbrk\aFS = \fsbroken \\
&\cxynv\aFS = 
   \begin{cases}
   \fsbroken &\mbox{if~} \FS=\fsbroken\\
   \fsbroken &\mbox{if~} [\FS(n)]\neq[x]\\
   \fsbroken &\mbox{if~} \FS_{[y/n]} \mbox{~violates the tree property}\\
   \FS_{[y/n]} &\mbox{otherwise.}
   \end{cases}
\end{align*}
\end{mydef}

### 2016-10-08 p2/def-filesystem.tex
New notation for commands

\begin{mydef}[$n\descendant m$]
On $\setn$ the \emph{ancestor / descendant} relation is the
strict partial ordering determined by the $\parent$ function.
We write $n\descendant m$ if $n$ is the ancestor of $m$,
that is, $n=\parent^a(m)$ for some integer $a\ge 1$.
% or the path name of $n$ is an initial segment of that of $m$. 
We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
\end{mydef}

\begin{mydef}[$n\unrel m$]
We write $n\unrel m$, or $n$ and $m$ are \emph{incomparable}
if $n\not\descendantEq m$ and $n\not\ancestorEq m$;
that is, incomparable nodes are on different branches or on different trees.
% none of the path names describing their location is an initial segment of the other.
\end{mydef}

Every working filesystem has a so-called \emph{tree property}, which means that
if the filesystem is not empty at a node, and the node has a parent,
then there must be a directory at the parent node.
To model this, in $\setv$ we select another special value
to represent directories, as we assume that apart from their location
in the filesystem, all directories are equal.
We do this because, as Bill Zissimopoulos pointed 
out \cite{BZ},
we often do not want to consider metadata stored in
directories (e.g. permission settings) during synchronization,
as these are not generally understood well by users,
and, if needed, conflict resolution on these settings can be easily automated.
We will also see that this assumption makes it possible
to define a maximal reconciliation algorithm.

Let therefore the value representing directories be $\vald$,
and let us define subsets of $\setv$ for each type of value:
let $\setd$ be $\{\vald\}$, let $\setb$ be $\{\empt\}$, 
and let $\setf$ contain all remaining values that represent
different file contents together with any metadata associated with them:
\[ \setv = \setb \cup \setf \cup \setd. \]

The tree property can then be defined as
\begin{mydef}[Tree property]
\begin{align*}
\forall n\in\setn:{} &\FS(n) \neq \empt \\
&\quad\wedge \parent(n) \neq \topnode \\
&\Rightarrow \FS(\parent(n)) \in \setd. 
\end{align*}
\end{mydef}
This means that as we move down from the root of a tree of nodes,
the types of values we encounter in the filesystem can only change according to the
transition diagram in \cref{fig_transition}, from directories ($\cchard$) to files ($\ccharf$)
to empty nodes ($\ccharb$).

\begin{figure}[htb]
\input{fig-type-transition}
\caption{Transitions between types of values from the root of a tree in a filesystem}\label{fig_transition}
\end{figure}

In this paper, $\FS$ and $\GS$ denote filesystems,
and $n$, $m$ and $o$ are nodes in $\setn$.
We use $\valf$ for an arbitrary element in $\setf$, 
and by $\valvx$ we mean a value of type $X$ in $\setvx{X}$.

>>>>

\begin{mydef}[$n\descendant m$]
On $\setn$ the \emph{ancestor / descendant} relation is the
strict partial ordering determined by the $\parent$ function.
We write $n\descendant m$ if $n$ is the ancestor of $m$,
that is, $n=\parent^i(m)$ for some integer $i\ge 1$.
% or the path name of $n$ is an initial segment of that of $m$. 
We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
\end{mydef}

\begin{mydef}[$n\unrel m$]
We write $n\unrel m$, or $n$ and $m$ are \emph{incomparable}
iff $n\not\descendantEq m$ and $n\not\ancestorEq m$;
that is, incomparable nodes are on different branches or on different trees.
% none of the path names describing their location is an initial segment of the other.
\end{mydef}

Every working filesystem has a so-called \emph{tree property}, which means that
if the filesystem is not empty at a node, and the node has a parent,
then there must be a directory at the parent node.
To model this, we differentiate between files, directories, and the
empty value in $\setv$, and introduce the equivalence relation
$\typeeq$.

\begin{mydef}[Equivalence by type: $\typeeq$]
We write $v_1\typeeq v_2$ for $v_1,v_2\in\setv$ if $v_1$ and $v_2$ are both files,
are both directories, or are both $\empt$.
In other words, if $\setf$ is the set of file values and $\setd$ is the set of directories, then
with $\{\empt\}$ they form a partition of $\setv$:
\[ \setv/{\typeeq} = \{\setd,\setf,\{\empt\}\}. \]
\end{mydef}

As usual, we write $[v]$ for the equivalence class of $v$, which is its type.
We also regard all file contents including all metadata to be included in the values in $\setf$.

The formal definition of the tree property is therefore
\begin{mydef}[Tree property]
\begin{align*}
\forall n\in\setn:{} &\FS(n) \neq \empt \\
&\quad\wedge \parent(n) \neq \topnode \\
&\Rightarrow \FS(\parent(n)) \in \setd. 
\end{align*}
\end{mydef}

To avoid the proliferation of edge cases, we will furthermore suppose that
$|\setd|=1$, that is, apart from their location, all directories are equal;
and use $\vald$ to denote the single value of the directory type.
In appendix TODO we describe why it can be a sensible choice
for actual synchronizers, and we also present an encoding that makes it possible
to extend our results to the $|\setd|>1$ case.

%% TODO
% % To model this, in $\setv$ we select another special value
% % to represent directories, as we assume that apart from their location
% % in the filesystem, all directories are equal.
% % We do this because, as Bill Zissimopoulos pointed 
% % out \cite{BZ},
% % we often do not want to consider metadata stored in
% % directories (e.g. permission settings) during synchronization,
% % as these are not generally understood well by users,
% % and, if needed, conflict resolution on these settings can be easily automated.
% % We will also see that this assumption makes it possible
% % to define a maximal reconciliation algorithm.

% This means that as we move down from the root of a tree of nodes,
% the types of values we encounter in the filesystem can only change according to the
% transition diagram in \cref{fig_transition}, from directories ($\cchard$) to files ($\ccharf$)
% to empty nodes ($\ccharb$).
% 
% \begin{figure}[htb]
% \input{fig-type-transition}
% \caption{Transitions between types of values from the root of a tree in a filesystem}\label{fig_transition}
% \end{figure}

In this paper, $\FS$ and $\GS$ denote filesystems,
and $n$, $m$ and $o$ are nodes in $\setn$.
We will write $\valf$ for an arbitrary element in $\setf$.

### 2016-10-08 p2/ordering.tex
New notation for commands

We also assume that they do not contain the same commands.
Without loss of generality, we can assume
that $A$
contains $\cxynv$, and $B$ either contains a different command
$\czwnv$ on $n$, or no command on $n$ at all.
As $A$ is simple, we know that $\cxynv$ is not an assertion command,
and therefore $X\neq Y$ and $\FS(n)\neq\valvy$ as it has type $X$.
If so, then if $B$ has no command on $n$, then $B\aFS(n)=\FS(n)$ and
$A$ and $B$ cannot be equivalent.
Otherwise we know that $Z=X$ as $B$ does not break $\FS$ either,
and that $\valvw=\valvy$ and therefore $W=Y$ as $B\aFS(n)$ must
be $\valvy$ and $B$ only has one command on $n$.
However, then $\czwnv=\cxynv$, which is a contradiction.
\end{proof}

>>>>

We also assume that they do not contain the same commands.
Without loss of generality, we can assume
that $A$
contains $\cxynv$, and $B$ either contains a different command
$\czwnv$ on $n$, or no command on $n$ at all.
As $A$ is simple, we know that $\cxynv$ is not an assertion command,
and therefore $[x]\neq [y]$ and $\FS(n)\neq y$ as $[\FS(n)]=[x]$.
If so, then if $B$ has no command on $n$, then $B\aFS(n)=\FS(n)$ and
$A$ and $B$ cannot be equivalent.
Otherwise we know that $[z]=[x]$ as $B$ does not break $\FS$ either,
and that $w=y$ as $B\aFS(n)$ must
be $y$ and $B$ only has one command on $n$.
However, then $\czwnv=\cxynv$, which is a contradiction.
\end{proof}
